---
title: "Statistical models: linking data to theory"
---

## Setup environment

```{r}
#| output: false
library(tidyverse)
library(easystats)
library(ggformula)
```

## Class 1: Introduction

<https://youtu.be/b2PyeRu53OU>

What is a statistical model?

A statistical model is a mathematical representation of a process that generates data, according to some theory.

Thus, a statistical model is a way to link data to theory, i.e., a hypothesis about how a given data set was generated.

Deterministic vs stochastic mathematical model.

## Class 2: Statistical models

XXX

## Generalized linear models

```{r}
library(titanic)
```

```{r}
m0 <- glm(Survived ~ 1, data = titanic_train, family = binomial)

summary(m0)
```

```{r}
plogis(parameters(m0)$Coefficient)
```

```{r}
mean(titanic_train$Survived)
```

```{r}
qlogis(mean(titanic_train$Survived))
```

```{r}
m1 <- glm(Survived ~ 1 + Sex, data = titanic_train, family = binomial)

summary(m1)
```

```{r}
estimate_means(m1, "Sex")
```

```{r}
m2 <- glm(Survived ~ 1 + Sex + factor(Pclass), data = titanic_train, family = binomial)

summary(m2)
```

```{r}
estimate_means(m2, c("Sex", "Pclass"))
```
